The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-08-23 src/cover-letter.tex
Version for Scientific Reports.

\begin{letter}{%
        To the Editors of\\
        Nature Human Behaviour \\
    }

@@

    Many thanks for considering our manuscript for possible publication in
    \textit{Nature Human Behavior}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership. On way to view the manuscript is as taking the same
    basic approach as the work by Aleta et al.---published a year ago in this
    journal---and demonstrating its usefulness for modelling and understanding the
    spread of the virus under different policies.

>>>>

\begin{letter}{%
        To the Editors of\\
        Scientific Reports \\
    }

@@

    Many thanks for considering our manuscript for possible publication in
    \textit{scientific reports}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership. We make both methodological and substantive
    contributions.
